---
title: "数据集探索"
output: html_notebook
---

Read the data and get overview. 
```{r}
library(data.table)
dt.train <- fread('train.csv')
dt.test <- fread('test.csv')
dt <- rbindlist(list(dt.train, dt.test), fill=T)
str(dt)
```

Extract the title information.
```{r}
dt$Title <- gsub('(.*, )|(\\..*)', '', dt$Name)
rare_title <- c('Capt', 'Col', 'Don', 'Dona', 'Dr', 'Jonkheer', 'Lady', 
                'Major', 'Rev', 'Sir', 'the Countess')
dt[Title %in% rare_title]$Title <- 'Rare Title'
dt[Title == 'Mlle' | Title == 'Ms']$Title <- 'Miss'
dt[Title == 'Mme']$Title <- 'Mrs'
table(dt$Sex, dt$Title)
```

Combine the family size information.
```{r}
library(ggplot2)
dt$Fsize <- dt$SibSp + dt$Parch + 1
ggplot(data=dt[!is.na(Survived)], aes(x=Fsize, fill=factor(Survived))) + 
  geom_bar(position="dodge") +
  labs(x="Family Size")
dt$Surname <- sapply(dt$Name, function(x) strsplit(x, split = '[,.]')[[1]][1])
dt$Family <- paste(dt$Survived, dt$Fsize, '_')
```

Discretize the family size. 
```{r}
dt$FsizeD <- ''
dt[Fsize==1]$FsizeD <- 'singlenton'
dt[Fsize>1 & Fsize<5]$FsizeD <- 'small'
dt[Fsize>4]$FsizeD <- 'large'
mosaicplot(table(dt$FsizeD, dt$Survived), main='Family size for survive', shade=T)
```

```{r}
dt$Deck <- factor(sapply(dt$Cabin, function(x) strsplit(x,NULL)[[1]][1]))
ggplot(dt[Embarked!=""], aes(x=Embarked, y=Fare, fill=factor(Pclass))) +
  geom_boxplot() +
  geom_hline(aes(yintercept=80), colour='red')
# imputation
dt[Embarked==""]$Embarked <- 'C'
```

```{r}
ggplot(dt[Pclass==3 & Embarked=="S"], aes(x=Fare)) +
  geom_density() +
  geom_vline(aes(xintercept=median(Fare, na.rm=T)),colour='red',linetype='dashed')
dt[is.na(Fare)]$Fare <- median(dt[Pclass==3 & Embarked=="S"]$Fare,na.rm=T)
```

Look at the other missing items.
```{r}
sapply(dt, function(x) sum(is.na(x)))
```

Imputate the missing item with mice package.
```{r}
library(mice)
library(randomForest)
dt$Deck <- factor(dt$Deck, exclude=NA)
mice_mod <- mice(dt[,!names(dt) %in% c('PassengerId','Name','Ticket','Cabin','Family','Surname','Survived'),with=F], method='rf')
```

Compare the imputation result with before.
```{r}
mice_output <- complete(mice_mod)
par(mfrow=c(1,2))
hist(dt$Age, main='Age: Original', col='darkgreen')
hist(mice_output$Age, main='Age: Imputation', col='lightgreen')
dt$Age <- mice_output$Age
dt$Deck <- mice_output$Deck
```

Analyze the relationship between age and survived.
```{r}
ggplot(dt[1:891], aes(Age, fill=factor(Survived))) +
  geom_histogram() +
  facet_grid(.~Sex)
```

Distinguish the child and adult.
```{r}
dt$Child[dt$Age<18] <- 'Child'
dt$Child[dt$Age>=18] <- 'Adult'
table(dt$Child, dt$Survived)
```

Distinguish the mother and not mother.
```{r}
dt$Mother <- 'Not Mother'
dt[Sex=='female' & Age>18 & Parch>0 & Title!='Miss']$Mother <- 'Mother'
table(dt$Mother, dt$Survived)
```

Split into train and test set.
```{r}
factor.set <- c('Sex','Embarked','Title','FsizeD','Child','Mother')
dt[,(factor.set):=lapply(dt[,factor.set,with=F], function(x) as.factor(x))]
dt.train <- dt[1:891]
dt.test <- dt[892:1309]
```

Building the model.
```{r}
set.seed(123)
rf.model <- randomForest(factor(Survived) ~ Pclass+Sex+Age+SibSp+Parch+Fare+Embarked+Title+FsizeD+Child+Mother, data=dt.train)
plot(rf.model)
legend('topright', colnames(rf.model$err.rate), col=1:3, fill=1:3)
```

Analyze the importance.
```{r}
imp <- importance(rf.model)
varImp <- data.frame(var = row.names(imp),
                     imp = round(imp[,1],2))
ggplot(varImp, aes(x=reorder(var, imp), y=imp, fill=imp)) +
  geom_bar(stat='identity') +
  labs(x='var') +
  coord_flip()
```

Prediction!
```{r}
pred <- predict(rf.model, dt.test)
ret <- data.frame(PassengerId=dt.test$PassengerId, Survived=pred)
write.csv(ret, 'submission.csv', row.names=F)
```

